Democracy, Public Support, and Measurement Uncertainty

### 2021-07-13 paper/dcpo_demsupport.Rmd

mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))

@@

## Incorporating Uncertainty
Although measurement uncertainty has yet not attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, 360; @caughey_policy_2018, 254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey_policy_2018, 254].

Therefore, after we replicate the original analyses that used only the point estimates of democratic support, we incorporate the full distribution of the latent variable estimates.
To do this, we replicate the latent variable estimation from the original survey data, duplicate each article's analysis dataset 1,000 times, and assign to each a different random draw from the posterior distribution of public democratic support.
Then we perform each analysis repeatedly on its respective collection of datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
Our approach of incorporating uncertainty is analogous to @Blackwell2017a's multiple overimputation which corrects the Between imputation variance. 
We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, 215) as robuestness check [see Supplementary Appendix xx].

@@

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Liberal Democracy (Vdem)") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
    #scale_color_gb(palette = "digitMixed") +
    facet_wrap(~ type)

@@

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Public Support for Democracy") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
   # scale_color_gb(palette = "digitMixed") +
    facet_wrap( ~ type)

@@

# Replication with Alternative Methods Accounting for Uncertainty
```{r moc_estimates}

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))

@@

@@

```{r mocresult-pureAJPS}

df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
  pure_cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_pure_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
  result <- methodComposition1(df_pure_clsAjps,aMod)
})

names(result_pure_clsUncertain) <- c("pooled", "pooled-regime")

result_pure_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
  result <- methodComposition2(df_pure_clsAjps,aMod)
})
names(result_pure_clsUncertain_gmm) <- c("gmm", "gmm-regime")

mocresult_pureAJPS <- append(result_pure_clsUncertain, result_pure_clsUncertain_gmm)

saveRDS(mocresult_pureAJPS, file =here("output","estimates_moc_pureAJPS.RDS"))

```{r mocresult-expAJPS}

df_exp_clsAjps <- purrr::map(1:900, function(anEntry) {
  exp_cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_exp_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
  result <- methodComposition1(df_exp_clsAjps,aMod)
})

names(result_exp_clsUncertain) <- c("pooled", "pooled-regime")

result_exp_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
  result <- methodComposition2(df_exp_clsAjps,aMod)
})
names(result_exp_clsUncertain_gmm) <- c("gmm", "gmm-regime")

mocresult_expAJPS <- append(result_exp_clsUncertain, result_exp_clsUncertain_gmm)

saveRDS(mocresult_expAJPS, file =here("output","estimates_moc_expAJPS.RDS"))

```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}

result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["pooled"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["gmm"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original", "Uncertainty", "Uncertainty+Expanded Data")))

@@

###########Regime
result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["pooled-regime"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["gmm-regime"]]), model = "Uncertainty"),
 mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
)%>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data")))
terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))
plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
legend <- get_legend(plot_AJPS2)
plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)

@@

```{r mocresult-pureAPSR}

df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
  pure_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

mocresult_pureAPSR  <- map(ls_mod_apsrCLS, function(aMod){
  result <- methodComposition3(df_pure_clsAPSR,aMod)
})

names(mocresult_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(mocresult_pureAPSR, file = here::here("ouput","estimates_moc_pureAPSR.RDS"))

@@

```{r mocresult-expAPSR}

df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
  exp_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

mocresult_expAPSR <- map(ls_mod_apsrCLS, function(aMod){
  result <- methodComposition3(df_exp_clsAPSR,aMod)
})

names(mocresult_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expAPSR.RDS"))

@@

```{r plot-mocAJPS, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["pooled1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["fd1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data"))
  )

@@

############################ Regime specified####

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

>>>>

@@

## Incorporating Uncertainty
Although measurement uncertainty has yet not attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, 360].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey_policy_2018, 254].

Therefore, after we replicate the original analyses that used only the point estimates of democratic support, we incorporate the full distribution of the latent variable estimates.
To do this, we replicate the latent variable estimation from the original survey data, duplicate each article's analysis dataset 1,000 times, and assign to each a different random draw from the posterior distribution of public democratic support.
Then we perform each analysis repeatedly on its respective collection of datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
Our approach of incorporating uncertainty is similar in the logic of @Blackwell2017a's multiple overimputation, that is, creating multiple data set from the posterior distribution of the true latent value, applying analysis model for each dataset, and then averaging results by using Rubin's rule.

@@

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Liberal Democracy (Vdem)") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
    scale_color_gb(palette = "digitMixed") +
    facet_wrap(~ type)

@@

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Public Support for Democracy") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
    scale_color_gb(palette = "digitMixed") +
    facet_wrap( ~ type)

@@

# Replication with Alternative Methods Accounting for Uncertainty
```{r MocclaassenUncertaintyAJPS}
load(here("data","cls_ajps.rda"))

df_cls <- purrr::map(1:900, function(anEntry) {
  cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

ls_iv <- c("plm::lag(SupDem_trim, 1)",                         
           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") ##all use trim
ls_method <- c("plm", "pgmm")
ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + 
              plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + 
              plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")

ls_mod <- c(
  glue("plm({ls_eq}, model = 'pooling', data = aData)"),
  glue(
    "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
  )
)

result_clsUncertain  <- map(ls_mod[1:2], function(aMod){
  result <- methodComposition1(df_cls,aMod)
})

names(result_clsUncertain) <- c("pooled", "pooled-regime")

result_clsUncertain_gmm  <- map(ls_mod[3:4], function(aMod){
  result <- methodComposition2(df_cls,aMod)
})
names(result_clsUncertain_gmm) <- c("gmm", "gmm-regime")

result_clsUncertain_whole <- append(result_clsUncertain, result_clsUncertain_gmm)

saveRDS(result_clsUncertain_whole, file =here("output","clsAJPS_uncertainty.RDS"))

@@

```{r MocdcpoUncertaintyAJPS}
load(here("data","dcpo_ajps.rda"))

df_dcpo <- purrr::map(1:900, function(anEntry) {
  dcpo_ajps[[anEntry]] %>%     #original data has include theta_dem_trim
    plm::pdata.frame(index = c("country", "year"))
})

ls_iv <- c("plm::lag(theta_trim, 1)", 
           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1)") #use trimed data
ls_method <- c("plm", "pgmm")
ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)") 
ls_mod <- c(
  glue("plm({ls_eq}, model = 'pooling', data = aData)"),
  glue(
    "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
  )
)

result_dcpoUncertain  <- map(ls_mod[1:2], function(aMod){
  result <- methodComposition1(df_dcpo,aMod)
})

names(result_dcpoUncertain) <- c("pooled", "pooled-regime")

result_dcpoUncertain_gmm  <- map(ls_mod[3:4], function(aMod){
  result <- methodComposition2(df_dcpo,aMod)
})

names(result_dcpoUncertain_gmm) <- c("gmm", "gmm-regime")

result_dcpoUncertain_whole <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)

saveRDS(result_dcpoUncertain_whole, file =here("output","dcpoAJPS_uncertainty.RDS"))

@@

```{r visualizedMocUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertain_whole <- readRDS(here("output", "clsAJPS_uncertainty.RDS"))
result_dcpoUncertain_whole <- readRDS(here("output", "dcpoAJPS_uncertainty.RDS"))

result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["pooled"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled"]]), model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["gmm"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm(result_dcpoUncertain_whole[["gmm"]]), model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/uncertainty", "DCPO")))

@@

###########Regime
result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["pooled-regime"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled-regime"]]), model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["gmm-regime"]]), model = "Claassen w/uncertainty"),
    mutate(MOCsumm(result_dcpoUncertain_whole[["gmm-regime"]]), model = "DCPO")
)%>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a","Claassen w/uncertainty", "DCPO")))
terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))
plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
legend <- get_legend(plot_AJPS2)
plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)

@@

```{r claassenMocUncertaintyAPSR}
load(here("data", "pure_cls_apsr.rda")) #use pure_cls_apsr instead of cls_apsr
load(here("data", "exp_cls_apsr.rda")) #use exp_cls_apsr instead of cls_apsr

df_clsAPSR <- purrr::map(1:900, function(anEntry) {
  pure_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

df_our_clsAPSR <- purrr::map(1:900, function(anEntry) {
  exp_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector() ##Change theta to SupDem_trim

ls_ivFD <- c("Libdem_z",
             "Polyarchy_z + Liberal_z")
ls_ctrlFD <- c("", " + Corrup_TI_z")
ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()
ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
)

result_clsUncertain  <- map(ls_mod, function(aMod){
  result <- methodComposition3(df_clsAPSR,aMod)
})  #claassen's data

result_our_clsUncertain  <- map(ls_mod, function(aMod){
  result <- methodComposition3(df_our_clsAPSR,aMod)
})   ##our expanded data

names(result_clsUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

names(result_our_clsUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_clsUncertain, file = here::here("ouput","clsAPSR_uncertainty.RDS"))

saveRDS(result_our_clsUncertain, file = here::here("ouput","our_clsAPSR_uncertainty.RDS"))

@@

```{r  dcpoMocUncertaintyAPSR}
load(here("data","dcpo_apsr.rda"))
df_dcpoUncertainAPSR <- purrr::map(1:900, function(anEntry) {
  dcpo_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
ls_eqECM <- glue("diff(theta_trim, lag = 1) ~ plm::lag(theta_trim, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector()

ls_ivFD <- c("Vdem_libdem_z",
             "Vdem_polyarchy_z + Vdem_liberal_z")
ls_ctrlFD <- c("", " + corruption_z")
ls_eqFD <- glue("theta_trim ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()

ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
)

result_dcpoUncertain  <- map(ls_mod, function(aMod){
  result <- methodComposition3(df_dcpoUncertainAPSR,aMod)
})

names(result_dcpoUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_dcpoUncertain, file =here("output","dcpoAPSR_uncertainty.RDS"))

@@

```{r visualizedMocUncertainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

#result_clsUncertain <- readRDS(here("output","clsAPSR_uncertainty.RDS"))
result_clsUncertain <- readRDS(here("output","our_clsAPSR_uncertainty.RDS"))
result_dcpoUncertain <- readRDS(here("output","dcpoAPSR_uncertainty.RDS"))
result_clsAPSR <- readRDS(here("output","estimates_clsMeanAPSR.RDS"))

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Claassen 2020b"),
  mutate(MOCsumm2(result_clsUncertain[["pooled1"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm2(result_dcpoUncertain[["pooled1"]]), model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Claassen 2020b"),
  mutate(MOCsumm2(result_clsUncertain[["fd1"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm2(result_dcpoUncertain[["fd1"]]), model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020b","Claassen w/uncertainty", "DCPO"))
  )

@@

############################ Regime specified####
result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Claassen 2020b"),
  mutate(MOCsumm2(result_clsUncertain[["pooled-regime1"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm2(result_dcpoUncertain[["pooled-regime1"]]), model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Claassen 2020b"),
  mutate(MOCsumm2(result_clsUncertain[["fd-regime1"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm2(result_dcpoUncertain[["fd-regime1"]]), model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020b","Claassen w/uncertainty", "DCPO"))
  )
terms3 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")
